SDR enhancement by clouds

### 2024-03-21 article/article.Rmd
Commit 2024-03-21 20:16

@@

In order to identify CE cases, we used a modeled approximation of the expected clear
sky GHI.  Because of the lack of observational data for the whole period, we used
some long term climatological data for the main factors responsible for the
attenuation of the broadband downward solar radiation in the atmosphere, which are
mainly the aerosols and the water vapors. Fortunately, our site participates in the
Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998], as we operate a Cimel
photometer since 2003, collocated with the CM-21 pyranometer.  The mean monthly
aerosol optical depth (AOD) on different wavelengths is provided by AERONET along
with the equivalent water column height in the atmosphere.  The simulation of the
clear sky radiation was performed by the well established radiation transfer model
Libradtran [@Emde2016], a similar modeling approach was also used by @Vamvakas2020.

@@

@@

## Criteria for enhancement identification

Initially, we try to implement criteria of CE identification similar to  .

>>>>

## Cloud enhancement detection

To be able to detect the CE cases, we had establish a baseline, above which we can
characterize each data point as enhancement event, by estimating the occurring over
irradiance.  To have an estimation and a first insight on the phenomenon, we
experimented with two simpler approaches as the reference.  The Haurwitz's model
[@Haurwitz1945], which is as simple clear sky we have previous adjusted and had good
fit with our data [@Natsis2023], and the TSI at the top of the atmosphere.  For both
cases we tested using an appropriate relative threshold and/or an constant offset.
The initial results, showed that we can detect a big portion of the CE events. But it
was evident, by inspecting the daily plot of irradiance, that changes on the
atmospheric conditions introduced numerous false positive and false negative results.

Initially, we try to implement a simpler approach for the clear sky reference,
without the use of a radiation transfer model. We experimented with a

@@

In order to identify CE cases, we used a modeled approximation of the expected clear
sky GHI.  Because of the lack of observational data for the whole period, we used
some long term climatological data for the main factors responsible for the
attenuation of the broadband downward solar radiation in the atmosphere, which are
mainly the aerosols and the water vapors. Fortunately, our site participates in the
Aerosol Robotic Network (AERONET) [@Giles2019; @Buis1998], as we operate a Cimel
photometer since 2003, collocated with the CM-21 pyranometer.  The mean monthly
aerosol optical depth (AOD) on different wavelengths is provided by AERONET along
with the equivalent water column height in the atmosphere.  The simulation of the
clear sky radiation was performed by the well established radiation transfer model
Libradtran [@Emde2016], a similar modeling approach, was also used by @Vamvakas2020.

@@

## Criteria for cloud enhancement identification

@@

### 2024-03-21 article/article.tex
Commit 2024-03-21 20:16

@@

In order to identify CE cases, we used a modeled approximation of the expected clear
sky GHI. Because of the lack of observational data for the whole period, we used
some long term climatological data for the main factors responsible for the
attenuation of the broadband downward solar radiation in the atmosphere, which are
mainly the aerosols and the water vapors. Fortunately, our site participates in the
Aerosol Robotic Network (AERONET) (Giles et al. 2019; Buis et al. 1998), as we operate a Cimel
photometer since 2003, collocated with the CM-21 pyranometer. The mean monthly
aerosol optical depth (AOD) on different wavelengths is provided by AERONET along
with the equivalent water column height in the atmosphere. The simulation of the
clear sky radiation was performed by the well established radiation transfer model
Libradtran (Emde et al. 2016), a similar modeling approach was also used by Vamvakas, Salamalikis, and Kazantzidis (2020).

@@

@@

\hypertarget{criteria-for-enhancement-identification}{%
\subsection{Criteria for enhancement identification}\label{criteria-for-enhancement-identification}}

Initially, we try to implement criteria of CE identification similar to .

@@

>>>>

\hypertarget{cloud-enhancement-detection}{%
\subsection{Cloud enhancement detection}\label{cloud-enhancement-detection}}

To be able to detect the CE cases, we had establish a baseline, above which we can
characterize each data point as enhancement event, by estimating the occurring over
irradiance. To have an estimation and a first insight on the phenomenon, we
experimented with two simpler approaches as the reference. The Haurwitz's model
(Haurwitz 1945), which is as simple clear sky we have previous adjusted and had good
fit with our data (Natsis, Bais, and Meleti 2023), and the TSI at the top of the atmosphere. For both
cases we tested using an appropriate relative threshold and/or an constant offset.
The initial results, showed that we can detect a big portion of the CE events. But it
was evident, by inspecting the daily plot of irradiance, that changes on the
atmospheric conditions introduced numerous false positive and false negative results.

Initially, we try to implement a simpler approach for the clear sky reference,
without the use of a radiation transfer model. We experimented with a

@@

In order to identify CE cases, we used a modeled approximation of the expected clear
sky GHI. Because of the lack of observational data for the whole period, we used
some long term climatological data for the main factors responsible for the
attenuation of the broadband downward solar radiation in the atmosphere, which are
mainly the aerosols and the water vapors. Fortunately, our site participates in the
Aerosol Robotic Network (AERONET) (Giles et al. 2019; Buis et al. 1998), as we operate a Cimel
photometer since 2003, collocated with the CM-21 pyranometer. The mean monthly
aerosol optical depth (AOD) on different wavelengths is provided by AERONET along
with the equivalent water column height in the atmosphere. The simulation of the
clear sky radiation was performed by the well established radiation transfer model
Libradtran (Emde et al. 2016), a similar modeling approach, was also used by Vamvakas, Salamalikis, and Kazantzidis (2020).

@@

\hypertarget{criteria-for-cloud-enhancement-identification}{%
\subsection{Criteria for cloud enhancement identification}\label{criteria-for-cloud-enhancement-identification}}

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-Haurwitz1945}{}}%
Haurwitz, Bernhard. 1945. {``Insolation in {Relation} to {Cloudiness} and {Cloud} {Density}.''} \emph{Journal of Meteorology} 2 (September): 154--66.
